Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-05-06 manuscript_results.Rmd
update

# Assuming merged_data already includes the necessary columns: model and percentage_improveme
# Create the map plot for 1 Week Ahead with best models and percentage improvement
ES_1WEEK <- ggplot(W1_map) +
  geom_sf(aes(fill = AUTO_AVG)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("Mean WIS on each state (W1)") +
  theme_light() +
  theme(legend.position = "right") +
  geom_sf_text(data = W1_map, aes(label = round(AUTO_AVG,1)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE) +  # Display percentage improvement in each state
  labs(
    fill = "Value",  # Label for the legend
    subtitle = "Based on 2023 and 2024 influenza seasons"
    , 
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_1WEEK<- ES_1WEEK + coord_sf(xlim = x_limits, ylim = y_limits)

ES_1WEEK
ggsave(ES_1WEEK, height = 4.5, width = 6.5,  filename="Fig4A.jpg")  
```
2 weeks ahead

@@

# Assuming merged_data already includes the necessary columns: model and percentage_improveme
# Create the map plot for 1 Week Ahead with best models and percentage improvement
ES_2WEEK <- ggplot(W2_map) +
  geom_sf(aes(fill = AUTO_AVG)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("Mean WIS on each state (W2)") +
  theme_light() +
  theme(legend.position = "right") +
  geom_sf_text(data = W2_map, aes(label = round(AUTO_AVG,1)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE) +  # Display percentage improvement in each state
  labs(
    fill = "Value",  # Label for the legend
    subtitle = "Based on 2023 and 2024 influenza seasons"
        , 
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_2WEEK <-ES_2WEEK + coord_sf(xlim = x_limits, ylim = y_limits)

ES_2WEEK
ggsave(ES_2WEEK, height = 4.5, width = 6.5,  filename="Fig4B.jpg")  
```
3 weeks ahead

@@

# Assuming merged_data already includes the necessary columns: model and percentage_improveme
# Create the map plot for 1 Week Ahead with best models and percentage improvement
# Create the map plot for 1 Week Ahead with best models and percentage improvement
ES_3WEEK <- ggplot(W3_map) +
  geom_sf(aes(fill = AUTO_AVG)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("Mean WIS on each state (W3)") +
  theme_light() +
  theme(legend.position = "right") +
  geom_sf_text(data = W3_map, aes(label = round(AUTO_AVG,1)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE) +  # Display percentage improvement in each state
  labs(
    fill = "Value",  # Label for the legend
    subtitle = "Based on 2023 and 2024 influenza seasons"
        , 
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_3WEEK<- ES_3WEEK + coord_sf(xlim = x_limits, ylim = y_limits)

ES_3WEEK

ggsave(ES_3WEEK, height = 4.5, width = 6.5,  filename="Fig4C.jpg")  
```
4 weeks ahead

@@

ES_4WEEK <- ggplot(W4_map) +
  geom_sf(aes(fill = AUTO_AVG)) +
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", 
                       midpoint = 100, limits = c(0, 352)) +  
  ggtitle("Mean WIS on each state (W4)") +
  theme_light() +
  theme(legend.position = "right") +
  geom_sf_text(data = W4_map, aes(label = round(AUTO_AVG,1)),  
               size = 3,
               color = "black",
               check_overlap = TRUE) +
  labs(
    fill = "Value",  
    subtitle = "Based on 2023 and 2024 influenza seasons"
        , 
       x = "",
       y = ""
  )

@@

ES_4WEEK<-ES_4WEEK + coord_sf(xlim = x_limits, ylim = y_limits)

ES_4WEEK
ggsave(ES_4WEEK,height = 4.5, width = 6.5,  filename="Fig4D.jpg")  
```
Loading datasets for regression analysis

>>>>

ES_1WEEK <- ggplot(W1_map) +
  geom_sf(aes(fill = AUTO_AVG)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("1 Week Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W1_map, aes(label = round(AUTO_AVG,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "mean WIS",  
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_1WEEK<- ES_1WEEK + coord_sf(xlim = x_limits, ylim = y_limits)
ES_1WEEK
#ggsave(ES_1WEEK, height = 4.5, width = 6.5,  filename="Fig4A.jpg")  
```

2 weeks ahead

@@

ES_2WEEK <- ggplot(W2_map) +
  geom_sf(aes(fill = AUTO_AVG)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("2 Weeks Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W2_map, aes(label = round(AUTO_AVG,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "mean WIS",
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_2WEEK <-ES_2WEEK + coord_sf(xlim = x_limits, ylim = y_limits)
ES_2WEEK
#ggsave(ES_2WEEK, height = 4.5, width = 6.5,  filename="Fig4B.jpg")  
```

@@

ES_3WEEK <- ggplot(W3_map) +
  geom_sf(aes(fill = AUTO_AVG)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("3 Weeks Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W3_map, aes(label = round(AUTO_AVG,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "mean WIS",
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_3WEEK<- ES_3WEEK + coord_sf(xlim = x_limits, ylim = y_limits)
ES_3WEEK
#ggsave(ES_3WEEK, height = 4.5, width = 6.5,  filename="Fig4C.jpg")  
```
4 weeks ahead

@@

ES_4WEEK <- ggplot(W4_map) +
  geom_sf(aes(fill = AUTO_AVG)) +
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", 
                       midpoint = 100, limits = c(0, 352)) +  
  ggtitle("4 Weeks Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W4_map, aes(label = round(AUTO_AVG,0)),  
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +
  labs(
    fill = "mean WIS", 
       x = "",
       y = ""
  )

@@

ES_4WEEK<-ES_4WEEK + coord_sf(xlim = x_limits, ylim = y_limits)
ES_4WEEK
#ggsave(ES_4WEEK,height = 4.5, width = 6.5,  filename="Fig4D.jpg")  
```

Combine in a 2x2 grid

```{r}
# Combine in a 2x2 grid
combined_plot <- (ES_1WEEK | ES_2WEEK) /
                 (ES_3WEEK | ES_4WEEK) + 
  plot_annotation(
    title = "Figure X: Mean WIS for the 48 states in the contiguous U.S.",
    subtitle = "Results for the the 2022/2023 and 2023/2024 influenza seasons",
    theme = theme(plot.title = element_text(size = 16, face = "bold"),
                  plot.subtitle = element_text(size = 14))
  )
# Print
print(combined_plot)

# Save to file
ggsave("Fig4.jpg", combined_plot, width =12, height =7)

Loading datasets for regression analysis
